---
title: "Capstone Project Proposal"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Capstone Project Proposal

The goal of this project is to build a model that would predict the effect of temperature data on natural gas spot prices at the Henry Hub natural gas distribution hub in Erath, Louisiana.

## Problem Statement

Natural gas prices are very volatile and is somewhat dependent on daily temperatures for heating/cooling needs. A model that would quantify this effect would help natural gas companies balance their distribution and supply of natural gas drawdowns.

## End User
The client is any exploration & production company that produces and sells natural gas. 

## Data Sources

The EIA government website provides historical data for daily natural gas spot prices. By using an EIA provided API key, this data can be loaded into a .csv file for analysis. Weather Underground provides daily weather data for Erath, LA. A similar API call can be used to pull this data into another .csv file

## Action Plan
Using about 2 years' worth of spot price/weather data as our training set, we'll build a regression model that will help define the effect of weather data on spot prices. Then the model will be run over a test set of about 3 months of data to validate our model.

## Deliverables

All R markdown files and related documents will be uploaded to GitHub.
```{r cars}
summary(cars)
```



```{r pressure, echo=FALSE}
plot(pressure)
```

